Output Summary

### 2023-07-06 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Updates to for sim years on output plots

# replace the placeholder index names with the specific elements in question
no_mcmc_diags_Minam = lapply(discard_params, sub_index, pop = j_min) |>
  lapply(sub_index, LH_type = i_spring) |>
  lapply(sub_index, origin = o_hor) |>
  lapply(sub_index, year = ts_yrs) |>
  lapply(unique) |>
  unlist()

>>>>

# replace the placeholder index names with the specific elements in question
no_mcmc_diags_Minam = lapply(discard_params, sub_index, pop = j_min) |>
  lapply(sub_index, LH_type = i_spring) |>
  lapply(sub_index, origin = o_hor) |>
  lapply(sub_index, year = observable) |>
  lapply(unique) |>
  unlist()

### 2023-07-06 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Updates to for sim years on output plots

plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

@@

```{r yr1-ocean-surv-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

>>>>

plot_proc_qresid = function(qresid_param, year = observable, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

@@

```{r yr1-ocean-surv-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```
